---
title: "linear model from Web"
author: "Th3b0yn3xtd00r"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction
We predict a simulated strength score based on arm and grip strength. We will find three models and compare them. The response variable is numerical, and the explanatory variable is numerical, so we use the Num~Num helper file.
Among those three models, which one of these are best? using anova
In this analysis, we examine three regression models: Model1 (SIMSARM), Model2 (SIMSGRIP), and Model3 (SIMS~ARM+GRIP). We calculate the 95% prediction intervals for SIMS with GRIP set to 94 and ARM set to 88 for each model and perform ANOVA to compare Model1 with Model3 and Model2 with Model3.

## Model 1 SIM~ARMS

## Results
### Graphical Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

As the arm strength rises the simulations rises as well.
### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation between SIMS and the ARM strength we can see that we got 0.6860073.
The correlation is 0.69 which shows that arm strength is related to SIMS score.

### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The coefficient and the intercept is significant. Both the intercept and the coefficient of ARM strength are significantly different from zero.

<<<<<<< HEAD
### Prediction Interval


=======
# Prediction Interval
```{r}
newdata = data.frame(ARM=88,GRIP=94)
predict(model.1, newdata, interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIMS score.

## Model 2 SIM~GRIP

## Results
### Graphical Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```

The graph shows that show the grip strength goes up the simulation strength goes up as well.
As the grip strength increases the SIMS increases. The spread of the points around the regression line in the grip plot are more spread out, than the arm strength plot.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation between SIMS and the ARM strength we can see that we got 0.6398458.
The correlation is 0.64 which shows that arm strength is related to SIMS score.

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

Both the intercept and the coefficient of GRIP strength are significantly different from zero.

#### Prediction Interval

```{r}
newdata = data.frame(ARM=88,GRIP=94)
predict(model.2, newdata, interval="predict")
```

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
print(summary(model.3))
```

The graph shows that show the GRIP/ARM strength and goes up the simulation strength goes up as well.
As the GRIP/ARM strength increases the SIMS increases. The spread of the points around the regression line in the grip plot are more spread out, than the GRIP/ARM strength plot.

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation is 0.73 which shows that GRIP/ARM strength is related to SIMS score.

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The graph shows that show the GRIP/ARM strength and goes up the simulation strength goes up as well.
As the GRIP/ARM strength increases the SIMS increases. The spread of the points around the regression line in the grip plot are more spread out, than the GRIP/ARM strength plot.

#### predict model.3 at target point
  
```{r}
newdata = data.frame(ARM=88,GRIP=94)
predict(model.3, newdata, interval="predict")
```

The prediction interval is from 0.15 to -2.3 for SIMS score.

## Comparing nested models ANOVA Test


### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

I reject the null hypothesis because of how low the P-value is (0.0000049). model one is better than model two because of model; one rss score being lower than model two

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

Model three has lower rss score than model two therefore making it a smaller model

# Disscussion and Conclusion
Model three is the best one out of the three since it carries a lower rss than the others.
